Optimal (Multiway) Spatial Joins

### 2024-05-23 msj.tex
yufei

\extraspacing {\bf Step 2.} We are ready to explain how to produce $\J_1(R_1, ..., R_{k-2}, H, V)$ from $\Pi_{1:k-2}(\J_1(R_1, ...,$ $R_{k-2}, H, V))$. Our algorithm for this purpose will find a set $S$ satisfying
\myeqn{
    \J_1(R_1, ..., R_{k-2}, H, V) 
    \subseteq 
    S
    \subseteq 
    \J(R_1, ..., R_{k-2}, H, V). \label{eqn:hv:type1:S}
}
Recall that $\J(R_1, ..., R_{k-2}, H, V)$ is the result of the original H-V $k$-SJ problem, which has a size of $\out$. Only the $k$-tuples in $S$ that are of Type 1 will be reported. We will achieve the purpose in $O(n \log n + |S|)$ time.

@@

\noindent In Appendix~\ref{app:hv:type1:gen-S}, we prove that the set $S$ computed satisfies \eqref{eqn:hv:type1:S}, as desired. If we exclude the time to compute all the $\cross(r_a, B; H)$ and $\cross(r_b, B; V)$, the running time of the above algorithm is
\myeqn{
    O(1 + |\Pi_{1:k-2}(\J_1(R_1, ..., R_{k-2}, H, V))| + |S|) \nn
}
which is $O(1 + \out)$ because of \eqref{eqn:hv:type1:S}. In what follows, we will explain how to compute all the $\cross(r_a, B; H)$ in $O(n \log n + |S|)$ time. A symmetric algorithm can be used to compute

>>>>

\extraspacing {\bf Step 2.} We are ready to explain how to produce $\J_1(R_1, ..., R_{k-2}, H, V)$ from $\Pi_{1:k-2}(\J_1(R_1, ...,$ $R_{k-2}, H, V))$. Our algorithm for this purpose will find a set $S$ satisfying
\myeqn{
    \J_1(R_1, ..., R_{k-2}, H, V) 
    \subseteq 
    S
    \subseteq 
    \J(R_1, ..., R_{k-2}, H, V). \label{eqn:hv:type1:S}
}
Recall that $\J(R_1, ..., R_{k-2}, H, V)$ is the result of the original H-V $k$-SJ problem, which has a size of $\out$. Only the $k$-tuples in $S$ that are of Type 1 will be reported. We will achieve the purpose in $O(n \log n + |S|) = O(n \log n + \out)$ time.

@@

\noindent In Appendix~\ref{app:hv:type1:gen-S}, we prove that the set $S$ computed satisfies \eqref{eqn:hv:type1:S}, as desired. If we exclude the time to compute all the $\cross(r_a, B; H)$ and $\cross(r_b, B; V)$, the running time of the above algorithm is
\myeqn{
    O(1 + |\Pi_{1:k-2}(\J_1(R_1, ..., R_{k-2}, H, V))| + |S|) \nn
}
which is $O(1 + \out)$ because of \eqref{eqn:hv:type1:S}. In what follows, we will explain how to compute all the $\cross(r_a, B; H)$ in $O(n \log n + |S|)$ time. A symmetric algorithm can be used to compute all the $\cross(r_b, B; V)$ in the same complexity. This will then allow us to conclude that Step 2 can be done in $O(n \log n + |S|)$ time.
